Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{Byzantium version \YellowPaperVersionNumber{}}}

### 2018-02-08 Paper.tex
Intrinsic gas hyperlinks and mathrm: \hyperlink{G__txdatazero}{G_{\mathrm{txdatazero}}}, etc.

\hypertarget{self_destruct_set_wordy_defn}{}The tuple contents include $A_{\mathbf{s}}$, the self-destruct set: a set of accounts that will be discarded following the transaction's completion.\hypertarget{tx_log_series_wordy_defn}{} $A_{\mathbf{l}}$ is the log series: this is a series of archived and indexable `checkpoints' in VM code execution that allow for contract-calls to be easily tracked by onlookers external to the Ethereum world (such as decentralised application front-ends).\hypertarget{tx_touched_accounts_wordy_defn}{} $A_{\mathbf{t}}$ is the set of touched accounts, of which the empty ones are deleted at the end of a transaction.\hypertarget{refund_balance_defn_words}{} Finally there is $A_{\mathrm{r}}$, the refund balance, increased through using the \hyperlink{SSTORE}{{\small SSTORE}} instruction in order to reset contract storage to zero from some non-zero value. Though not immediately refunded, it is allowed to partially offset the total execution costs.

@@

\subsection{Execution}
\hypertarget{intrinsic_gas_g_0}{}We define intrinsic gas $g_0$, the amount of gas this transaction requires to be paid prior to execution, as follows:
\begin{align}
g_0 \equiv {} & \sum_{i \in T_{\mathbf{i}}, T_{\mathbf{d}}} \begin{cases} G_{txdatazero} & \text{if} \quad i = 0 \\ G_{txdatanonzero} & \text{otherwise} \end{cases} \\
{} & + \begin{cases} G_\text{txcreate} & \text{if} \quad T_{\mathrm{t}} = \varnothing \\ 0 & \text{otherwise} \end{cases} \\
{} & + G_{transaction}
\end{align}

where $T_{\mathbf{i}},T_{\mathbf{d}}$ means the series of bytes of the transaction's associated data and initialisation EVM-code, depending on whether the transaction is for contract-creation or message-call. $G_\text{txcreate}$ is added if the transaction is contract-creating, but not if a result of EVM-code. $G$ is fully defined in Appendix \ref{app:fees}.

>>>>

\hypertarget{self_destruct_set_wordy_defn}{}The tuple contents include $A_{\mathbf{s}}$, the self-destruct set: a set of accounts that will be discarded following the transaction's completion.\hypertarget{tx_log_series_wordy_defn}{} $A_{\mathbf{l}}$ is the log series: this is a series of archived and indexable `checkpoints' in VM code execution that allow for contract-calls to be easily tracked by onlookers external to the Ethereum world (such as decentralised application front-ends).\hypertarget{tx_touched_accounts_wordy_defn}{} $A_{\mathbf{t}}$ is the set of touched accounts, of which the empty ones are deleted at the end of a transaction.\hypertarget{refund_balance_defn_words}{} Finally there is $A_{\mathrm{r}}$, the refund balance, increased through using the {\small SSTORE} instruction in order to reset contract storage to zero from some non-zero value. Though not immediately refunded, it is allowed to partially offset the total execution costs.

@@

\subsection{Execution}
\hypertarget{intrinsic_gas_g_0}{}We define intrinsic gas $g_0$, the amount of gas this transaction requires to be paid prior to execution, as follows:
\begin{align}
g_0 \equiv {} & \sum_{i \in T_{\mathbf{i}}, T_{\mathbf{d}}} \begin{cases} \hyperlink{G__txdatazero}{G_{\mathrm{txdatazero}}} & \text{if} \quad i = 0 \\ \hyperlink{G__txdatanonzero}{G_{\mathrm{txdatanonzero}}} & \text{otherwise} \end{cases} \\
{} & + \begin{cases} \hyperlink{Gtxcreate}{G_{\mathrm{txcreate}}} & \text{if} \quad T_{\mathrm{t}} = \varnothing \\ 0 & \text{otherwise} \end{cases} \\
{} & + \hyperlink{Gtransaction}{G_{\mathrm{transaction}}}
\end{align}

where $T_{\mathbf{i}},T_{\mathbf{d}}$ means the series of bytes of the transaction's associated data and initialisation EVM-code, depending on whether the transaction is for contract-creation or message-call. $G_{\mathrm{txcreate}}$ is added if the transaction is contract-creating, but not if a result of EVM-code. $G$ is fully defined in Appendix \ref{app:fees}.
